\cvsection{Experience}
\begin{cventries}
  \cventry
    {Senior Software Development Engineer}
    {Slice}
    {Bangalore, KA}
    {May 22 - Present}
    {
      \begin{cvitems}
        \item {Built DaaS(Data as a Service) that manages and serves data across multiple organizations while ensuring security and auditing measures are in place. It supprots postgres, mysql, DBX warehouse, async warehouse queries(on emr using airflow) datasources.}
        \item {Collaborated in a five-member team to develop UPI SWITCH for both PPI and TPAP which directly integrates with NPCI, Led the migration process from Juspay Switch to an in-house solution, streamlining UPI payments organization-wide.}
        \item {Built Sanction service that scrapes and provides search capabilities on public lists of sanctioned individuals.}
        \item {Built Avatar service that generates avatars in real-time based on a user's selfie or gmail picture during onboarding.}
        \item {Build NameMatch service that compares names from multiple sources to identify potential fraudsters.}
        \item {Migrated internal event streaming system from kinesis to Confluent Kafka.}
        \item {Implemented CI/CD for all services using github actions and aws codesuite.}
        \item {Refactored a legacy risk service that evaluates a user's purchasing power based on more than 100 factors.}
        \item {Built audit logging library in Golang, Python that has helped to maintain and manage the logic and infra.}
        \item {Migrated mongo database to a different cluster ensuring uninterrupted service and no impact on user experience.}
        \item {Integrated Sentry, APM, Xray, SonarQube, Swagger, and pre-commit hooks accross multiple srevice.}
      \end{cvitems}
    }
  
  \cventry
    {Software Development Engineer}
    {Swiggy(SuprDaily)}
    {Bangalore, KA}
    {Sep 21 - June 22}
    {
      \begin{cvitems}
        \item {Integrated algolia personalization to display items based on customer prior activity, cached to reduce latency.}
        \item {Enhanced the pricing platform to eliminate pricing discrepancies across different pages within the same session.}
        \item {Developed several feature like best selling items based on every region are displayed to some customer, this will be dynamically updated as on when customers orders.}
      \end{cvitems}
    }
  
  \cventry
    {Software Development Engineer}
    {Hyperverge Inc.}
    {Bangalore, KA}
    {June 20 - Sep 21}
    {
      \begin{cvitems}
        \item {Improved overall throughput by 60\% by splitting monolith into microservices.}
        \item {Used tools like sentry, opentelemetry as well as set up test environment to reduce 5xx error rates to almost zero.}
        \item {Developed polling machine learning models form s3 instead of committing to git, this has reduced effort of engineering team significantly.}
        \item {Developed an end to end service from scratch to blacklist devices, to block with multiple fraud attempts.}
        \item {Contributed and gained expertise in developing various components of document verification service, which analyzes and retrieves data. Built it from initial stages from defining the requirements to completion of deployment.}
        \item {Designed and developed end-to-end fully functional service which categorizes ID cards based on their quality into different buckets. Focused on various service aspects like scale and configurable design.}
      \end{cvitems}
    }

  \cventry
    {Software Development Intern}
    {Hyperverge Inc.}
    {Bangalore, KA}
    {Dec 19 - June 20}
    {
      \begin{cvitems}
        \item {Implemented an API to avoid data theft, by encrypting customer data to transfer them through various geographies, which is decrypted on the receiver's side.}
        \item {Developed a complete feature to mask user identification number, in national cards of various geographies. This has been made regional agnostic which generically solves the problem.}
        \item {Dockerised application which made deployment easy.}
        \item {Built an API which validates the user inputs with the data from the user uploaded ID card, this has been generalized to handle different kinds of information in the ID card. This helps customers avoid entering incorrect data.}
      \end{cvitems}
    }

\end{cventries}
