\cvsection{Projects}
\begin{cventries}
  \cventry
    { \textbf{ Automatically Calling Nearby Ambulance Service Incase Of Accident } }{}{}{}
    {
      \begin{cvitems}
        \item {Created a service which calls an ambulance in the event of an accident. Used Raspberry Pi, which retrieves the coordinates of the vehicle location and passes it to the server.}
        \item {Google Place API is used to retrieve the phone numbers of the ambulance services near to the accident location.}
        \item {Used SMS-Gatewayhub to message the coordinates of the accident location to the ambulance service providers, thereby bypassing the need for a phone call, Total TAT is lessthan a second.}
      \end{cvitems}
    }
  \cventry
    { \textbf{Games Developed} }{}{}{}
    {
      \begin{cvitems}
        \item {Created Snake, Pong, Bomber Man, Minesweeper games using Pygame(Python).}
        \item {Created endless-run game using unity in C-sharp.}
        \item {Developed a multiplayer shooting game that utilizes a UDP socket connection in Python and Pygame for the GUI. The game maintains its state on the client-side, which allows for the backend code to remain flexible and easily adaptable to multiple games.}
      \end{cvitems}
    }
  \cventry
    {\textbf{Timing Attacks On RSA}}{}{}{}
    {
      \begin{cvitems}
        \item {Analyzed how effective timing attacks can crack the key of RSA secured system.}
        \item {The analysis performed highlights the vulnerabilities of the RSA algorithm.}
      \end{cvitems}
    }
  \cventry
    { \textbf{ Hosted A Site - Checkmeter } }{}{}{}
    {
      \begin{cvitems}
        \item {Hosted a site using Flask. A custom link will be generated per user after signing up on this website. This link can be further forwarded to friends, in which they can enter data which is thereafter visible to the user.}
      \end{cvitems}
    }
  \cventry
    { \textbf{ Student Attendance Management System } }{}{}{}
    {
      \begin{cvitems}
        \item {Developed student attendance management system using Node.js, HTML, CSS, and JavaScript to streamline and automate attendance tracking for educational institutions}
      \end{cvitems}
    }
  
\end{cventries}